---
title: "3D Landscapes"
author: "Antonia Netzl"
date: "2023-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Base Map 
```{r}
setwd("~/Documents/smith/labbook/kimpel_paper/")
library(Racmacs)
library(tidyverse)
library(r3js)
library(ablandscapes)
library(htmlwidgets)

set.seed(100)
# set optimization nr to fit BA.4/5 position; optimization nr 56 gives upper BA.4/5

map <- read.acmap(file.path("data", "maps", "map-OmicronI+II+III-thresholded-single_exposure-P1m1-positioned.ace"))
lims <- Racmacs:::mapPlotLims(map, sera = FALSE)

lndscp_list <- readRDS(file.path("data", "landscape_fit", "biv_boosts_ags_all.rds"))
lndscp_sub <- readRDS(file.path("data", "landscape_fit", "biv_boosts_ags_sub.rds"))

plot(map, plot_labels = "antigens", label.offset = c(1.5),
label.size = 0.7,
  xlim = lims$xlim, ylim = lims$ylim)
```

## Antibody Landscapes
```{r}
lndscp_list$all
```

### 3x Vacc + bivalent BA.1 boost

```{r}
lndscp_list$`3x Vacc + bivalent BA.1 boost`
```

### 3x Vacc + conv. +  bivalent BA.1 boost

```{r}
lndscp_list$`3x Vacc + conv. + bivalent BA.1 boost`
```

### 3x Vacc + bivalent BA.4/5 boost

```{r}
lndscp_list$`3x Vacc + bivalent BA.4_5 boost`
```

### 3x Vacc + conv. +  bivalent BA.4/5 boost

```{r}
lndscp_list$`3x Vacc + conv. + bivalent BA.4_5 boost`
```

### Bivalent BA.1 boost, uninfected and infected

```{r}
lndscp_list$`BA.1`
```

### Bivalent BA.4/5 boost, uninfected and infected

```{r}
lndscp_list$`BA.4/5`
```

## Landscapes without fitting the new variants


```{r}
lndscp_list <- lndscp_sub
lndscp_list$all
```
### 3x Vacc + bivalent BA.1 boost

```{r}
lndscp_list$`3x Vacc + bivalent BA.1 boost`
```

### 3x Vacc + conv. +  bivalent BA.1 boost

```{r}
lndscp_list$`3x Vacc + conv. + bivalent BA.1 boost`
```

### 3x Vacc + bivalent BA.4/5 boost

```{r}
lndscp_list$`3x Vacc + bivalent BA.4_5 boost`
```

### 3x Vacc + conv. +  bivalent BA.4/5 boost

```{r}
lndscp_list$`3x Vacc + conv. + bivalent BA.4_5 boost`
```

### Bivalent BA.1 boost, uninfected and infected

```{r}
lndscp_list$`BA.1`
```

### Bivalent BA.4/5 boost, uninfected and infected

```{r}
lndscp_list$`BA.4/5`
```
